---
title: "index"
output: md_document
date: "2024-11-7"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

The Comparative Politics Seminar Series in the Department of Political and Social Sciences at the European University Institute is a venue for the presentation of work in progress by scholars from across the subfield of comparative politics. 

It usually takes place on Thursdays from 17:00 to 18:30 at Seminar Room 2, in Badia Fiesolana (Fiesole). See below or sync the [calendar](webcal://raw.githubusercontent.com/cpss-eui/cpss-eui.github.io/main/events.ics) for the exact location for each meeting. See [previous events](https://cpss-eui.github.io/old_events.html). 

The series is organized by [Elias Dinas](https://www.eui.eu/people?id=elias-dinas), [Simon Hix](https://simonhix.com//), and [Filip Kostelka](https://filipkostelka.com/), [Sascha Riaz](https://saschariaz.com/), with support by [Paloma Abril Poncela](https://palomaabril.github.io/) and [Carmen Ramirez Folch](https://www.eui.eu/people?id=carmen-ramirez-folch).


# Upcoming Events

```{r}
df <- readxl::read_excel("../../comparative-politics-seminar-series/speakers_2025.xlsx", sheet = 2)
df <- df[df$Subject!="TBD",]

colnames(df) <- tolower(colnames(df))
colnames(df) <- lapply(colnames(df), function(x) gsub("^\\s+|\\s+$", "", x))

df$start_date <- gsub("-", "", df$`start date`)
df$end_date <- gsub("-", "", df$`end date`)

df$title <- ifelse(df$title != "0", df$title, "Title TBD")
df$abstract <- ifelse(df$abstract != "0", df$abstract, "Abstract TBD")

df$location <- ifelse(grepl("\\?", df$location), "Location TBD", df$location)

df$subject <- gsub("CPSS: ", "", df$subject)
df$subject <- ifelse(is.na(df$subject), "TBD", df$subject)

df <- df[!is.na(df$start_date), ]
```

## Speakers during Winter/Spring 2025

```{r, results='asis'}
 df_ <- df[df$term %in% "Winter", ]

 for (i in 1:nrow(df_)) {
   weekday <- weekdays(as.Date(df_$`start date`[i]))
   year <- as.numeric(format(df_$`start date`[i], "%Y"))
   start_month <- format(strptime(df_$start_date[i], "%Y%m%d"), "%B")
   start_day <- format(strptime(df_$start_date[i], "%Y%m%d"), "%d")
   subject <- df_$subject[i]
   url <- df_$url[i]
   title <- df_$title[i]
   abstract <- df_$abstract[i]
   location <- df_$location[i]
   website <- df_$website[i]
  
   cat(paste0(weekday, " ", start_day, " ", start_month, " ", year, " | ", location,
             	"<p><strong><a href='", website, "'>", subject, "</a></strong></p>\n\n",
              "**", title, "**\n\n",
              "<details><summary>Abstract:</summary><p>", abstract, "</p></details>\n\n",
              "<hr>\n\n"))
 }

```
