```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
```

The Comparative Politics Seminar Series in the Department of Political and Social Sciences at the European University Institute is a venue for the presentation of work in progress by scholars from across the subfield of comparative politics. 

It usually takes place on Thursdays from 17:00 to 18:30 at Seminar Room 2, in Badia Fiesolana (Fiesole). See below or sync the [calendar](webcal://raw.githubusercontent.com/danielhurquijo/comparative-politics-seminar-series/main/events.ics?token=GHSAT0AAAAAACFEVOTAITIBGWCGEPBMNKD6ZG5ADIQ) for the exact location for each meeting. The event is in-person and on-line. Registration is required for online attendance. Attendance is generally restricted to members of the EUI community.

The series is organized by [Elias Dinas](https://www.eui.eu/people?id=elias-dinas), [Miriam Golden](https://www.miriamgolden.com/), [Simon Hix](https://simonhix.com//), and [Filip Kostelka](https://filipkostelka.com/), with support by [Daniel Urquijo](https://www.eui.eu/people?id=daniel-urquijo) and [Pau Grau](https://paugrau.cat/).


# Upcoming Speakers

## Speakers during Fall 2023

```{r}
df <- readxl::read_excel("../../comparative-politics-seminar-series/speakers.xlsx",
                         sheet = 2)%>%
  rename_all(., .funs=tolower)%>%
  rename_all(., .funs=str_trim)%>%
  mutate(start_date=str_replace_all(`start date`, "-", ""),
         end_date=str_replace_all(`end date`, "-", ""),
         title=case_when(title!="0"~title,
                         T~"Title TBD"),
         abstract=case_when(abstract!="0"~abstract,
                            T~"Abstract TBD"),
         location=case_when(!str_detect(location, "Seminar Room 2")~"Location TBD",
                            T~location),
         subject=str_remove(subject, "CPSS: "),
         subject=ifelse(is.na(subject), "TBD", subject))%>%
  filter(!is.na(start_date))
```


```{r, results='asis'}
df_ <- df%>%filter(term=="Fall")
for (i in 1:nrow(df_)) {
  weekday <- strftime(df_$`start date`[i],'%A')
  year <- year(df_$`start date`[i])
  start_month <- month(lubridate::as_date(df_$start_date[i]), label = TRUE, abbr = FALSE)
  start_day <- day(lubridate::as_date(df_$start_date[i]))
  subject <- df_$subject[i]
  url <- df_$url[i]
  title <- df_$title[i]
  abstract <- df_$abstract[i]
  location <- df_$location[i]
  website <- df_$website[i]
  
  cat(paste0(weekday, " ", start_day, " ", start_month, " ", year, " | ", location,
             	"<p><strong><a href='", website, "'>", subject, "</a></strong></p>\n\n",
             "**", title, "**\n\n",
             "<details><summary>Abstract:</summary><p>\n\n", abstract, "</p></details>\n\n",
             "<hr>\n\n"))
}
```

## Speakers during Winter 2024

```{r, results='asis'}
df_ <- df%>%filter(term=="Winter")

for (i in 1:nrow(df_)) {
  weekday <- strftime(df_$`start date`[i],'%A')
  year <- year(df_$`start date`[i])
  start_month <- month(lubridate::as_date(df_$start_date[i]), label = TRUE, abbr = FALSE)
  start_day <- day(lubridate::as_date(df_$start_date[i]))
  subject <- df_$subject[i]
  url <- df_$url[i]
  title <- df_$title[i]
  abstract <- df_$abstract[i]
  location <- df_$location[i]
  website <- df_$website[i]
  
  cat(paste0(weekday, " ", start_day, " ", start_month, " ", year, " | ", location,
             	"<p><strong><a href='", website, "'>", subject, "</a></strong></p>\n\n",
             "**", title, "**\n\n",
             "<details><summary>Abstract:</summary><p>", abstract, "</p></details>\n\n",
             "<hr>\n\n"))
}
```

## Speakers during Spring 2024

```{r, results='asis'}
df_ <- df%>%filter(term=="Spring")

for (i in 1:nrow(df_)) {
  weekday <- strftime(df_$`start date`[i],'%A')
  year <- year(df_$`start date`[i])
  start_month <- month(lubridate::as_date(df_$start_date[i]), label = TRUE, abbr = FALSE)
  start_day <- day(lubridate::as_date(df_$start_date[i]))
  subject <- df_$subject[i]
  url <- df_$url[i]
  title <- df_$title[i]
  abstract <- df_$abstract[i]
  location <- df_$location[i]
  website <- df_$website[i]
  
  cat(paste0(weekday, " ", start_day, " ", start_month, " ", year, " | ", location,
             	"<p><strong><a href='", website, "'>", subject, "</a></strong></p>\n\n",
             "**", title, "**\n\n",
             "<details><summary>Abstract:</summary><p>", abstract, "</p></details>\n\n",
             "<hr>\n\n"))
}

```
